\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}

\geometry{margin=1in}

% Formatting section headers
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]

\begin{document}

\begin{center}
    {\LARGE \textbf{Your Full Name}} \\
    \vspace{0.1cm}
    Email: your.email@example.com | Phone: +44 1234 567890 \\
    \href{https://linkedin.com/in/yourprofile}{LinkedIn} | \href{https://github.com/yourgithub}{GitHub} \\
\end{center}

\vspace{0.5cm}

\section*{Profile}
A proactive Software Engineering Graduate and ITIL-qualified Service Management Consultant, experienced in Python, Java, and web development frameworks like Django and Spring Boot. I have a proven track record of delivering custom solutions in SaaS environments, building and deploying web applications, and troubleshooting technical issues involving SSO, LDAP, and certificate management. Known for optimizing processes and streamlining operations through automation, I thrive in cross-functional roles combining technical expertise with stakeholder management.

\vspace{0.3cm}

\section*{Education}
\textbf{BSc (Hons) Software Engineering with Year Abroad (1st), University of Leicester} \\
2018 -- 2022 \\
\begin{itemize}[left=0.15cm]
    \item \textbf{Machine Learning Project:} Built a Raspberry Pi-based image recognition system using OpenCV and Flask. Achieved 95\% validation accuracy (Grade: 78\%).
    \item \textbf{SCRUM Team Project:} Led a team to develop a cross-platform expense tracking app using Flutter and Firebase (Grade: 75\%).
    \item \textbf{Survey Application:} Designed a Spring Boot JPA survey application with RESTful API and user authentication.
\end{itemize}

\textbf{Year Abroad, Sapienza Università Di Roma} \\
2020 -- 2021 \\
Studied Distributed Systems (80\%), Bioinformatics (90\%), and Classical Archaeology (93\%).

\vspace{0.3cm}

\section*{Technical Skills}
\begin{itemize}[left=0.15cm]
    \item \textbf{Languages:} Python, Java, JavaScript, HTML, CSS, LaTeX
    \item \textbf{Frameworks:} Django, Flask, Spring Boot, FreeMarker
    \item \textbf{Databases:} MySQL, Spring JPA
    \item \textbf{APIs:} REST APIs, MS Graph API, TOPdesk API
    \item \textbf{Authentication:} Spring Security, Django/Flask Authentication
    \item \textbf{Version Control:} Git, GitHub
    \item \textbf{Tools \& Environments:} Kubernetes, Docker
    \item \textbf{Testing \& Deployment:} PythonAnywhere, Unit Testing
    \item \textbf{Awards:} ITIL 4, Crest Award, Duke of York Award, Microsoft SQL Server Fundamentals, Generative AI \& Software Development Career Essentials
\end{itemize}

\vspace{0.3cm}

\section*{Professional Experience}
\textbf{Technical Product Support Consultant, TOPdesk UK} \\
2023 -- Present \\
\begin{itemize}[left=0.15cm]
    \item Recognized as the highest-performing team member, resolving tickets 40\% faster than the team average.
    \item Developed custom automation solutions using FreeMarker to streamline ticket workflows and client data integration.
    \item Troubleshot complex SaaS environments using Kubernetes and Elasticsearch, focusing on MS Graph mail integrations.
    \item Led the UK office during a data center migration, ensuring smooth transitions across international SaaS teams.
\end{itemize}

\textbf{Service Management Consultant, TOPdesk UK} \\
2021 -- 2023 \\
\begin{itemize}[left=0.15cm]
    \item Implemented a Service Catalogue, resulting in a 9\% revenue increase within two months post-launch.
    \item Coordinated agile sprints and led stakeholder meetings to ensure well-documented services.
    \item Built a custom solution to automate email communication flows, saving the client significant time.
\end{itemize}

\vspace{0.3cm}

\section*{Key Projects}
\textbf{Django Foosball Tracker App (2023)} \\
Developed a Django-based app for tracking and analyzing foosball match results, using PythonAnywhere and GitHub for CI/CD. Integrated AI-based performance analysis features for match statistics.

\textbf{Custom Reporting Tool (2023)} \\
Built a secure reporting tool using JavaScript, HTML, CSS, and the TOPdesk API to fetch real-time data. Implemented secure API authentication using session cookies.

\textbf{AI Cat Flap Detector (Final Year Project, 2022)} \\
Created a Flask application using OpenCV to detect when a cat approached a cat flap. Trained the machine learning model and deployed the app.

\textbf{Expense Tracking App, FDM (2021)} \\
Developed a cross-platform expense tracking app using Flutter and Firebase. Led sprint cycles and managed client communications for project success.

\vspace{0.3cm}

\section*{Interests}
3D Printing, Fitness, Traveling, Gardening

\end{document}
